Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-28 article.tex
typos

The human brain is a complex biological
organ made of 100 billions of neurons, each connected to 7000 other neurons on
average. Unfortunately, direct observation of the connectome, the wiring
diagram of the brain, is not yet technically feasible. Without being perfect,
calcium imaging currently allows the real-time and simultaneous observation of
neuron activities from thousands of neurons, producing individual time series
representing their fluorescence intensity. From these data, the connectome
inference problem amounts in retrieving the synaptic connections between
neurons on the basis of the fluorescence time series. This
problem is often difficult because of experimental issues, including
masking effects (i.e., some of the neurons are not observed or confounded with others), the low sampling rate of the optical device with respect to the
neural activity speed or the slow decay of fluorescence.

@@

We report in this apprendix the performance of the different methods compared
in the paper on 6 additional datasets provided by the challenge
organizers. These datasets, corresponding each to networks of 1000 neurons, are similar to
the \textit{normal} datasets except for one feature:
\begin{description}
\item[lowcon:] Similar network but with a lower number of connections per neuron on average.
\item[highcon:] Similar network but with a higher number of connections per neuron on average.
\item[lowcc:] Similar network but with a lower clustering coefficient on average.
\item[highcc:] Similar network but with a higher clustering coefficient on average.
\item[normal-3-highrate:] Same topology as \textit{normal-3} but with a higher firing frequency, i.e., with highly active neurons.
\item[normal-4-lownoise:] Same topology as \textit{normal-4} but with a better signal to noise ratio.
\end{description}

>>>>

The human brain is a complex biological
organ made of 100 billions of neurons, each connected to 7000 other neurons on
average. Unfortunately, direct observation of the connectome, the wiring
diagram of the brain, is not yet technically feasible. Without being perfect,
calcium imaging currently allows the real-time and simultaneous observation of
neuron activities from thousands of neurons, producing individual time series
representing their fluorescence intensity. From these data, the connectome
inference problem amounts to retrieving the synaptic connections between
neurons on the basis of the fluorescence time series. This
problem is often difficult because of experimental issues, including
masking effects (i.e., some of the neurons are not observed or confounded with others), the low sampling rate of the optical device with respect to the
neural activity speed or the slow decay of fluorescence.

@@

We report in this appendix the performance of the different methods compared
in the paper on 6 additional datasets provided by the challenge
organizers. These datasets, corresponding each to networks of 1000 neurons, are similar to
the \textit{normal} datasets except for one feature:
\begin{description}
\item[lowcon:] Similar network but with a lower number of connections per neuron on average.
\item[highcon:] Similar network but with a higher number of connections per neuron on average.
\item[lowcc:] Similar network but with a lower clustering coefficient on average.
\item[highcc:] Similar network but with a higher clustering coefficient on average.
\item[normal-3-highrate:] Same topology as \textit{normal-3} but with a higher firing frequency, i.e., with highly active neurons.
\item[normal-4-lownoise:] Same topology as \textit{normal-4} but with a better signal to noise ratio.
\end{description}
